### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@2b7a496ba0284efd37d0007167d17b9454d95631 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@31363ca119e8c6a3d54b557e6f16021940d3167d 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@20824b61006c91535f1d922d11fd9c9f00437fb3 🚀

%!TEX TS-program = xelatex
\documentclass[10pt,oneside]{article}

@@

\geometry{includemp,
            letterpaper,
            top=1.0in,
            bottom=2.510cm,
            inner=0.5in,
            outer=0.4in,
            marginparwidth=1.9in,
            marginparsep=0.3in}

@@

The first three fields are the title, language, and license. It's
probably advisable not to change these, and there are chances that the
logo on the PDF will not capture the values made here (this will have to
be, maybe, fixed at some point).

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{}
    \DataTypeTok{"title"}\FunctionTok{:} \StringTok{"Preprint template"}\FunctionTok{,}
    \DataTypeTok{"license"}\FunctionTok{:} \StringTok{"CC{-}BY"}\FunctionTok{,}
    \DataTypeTok{"language"}\FunctionTok{:} \StringTok{"en"}
\FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

>>>>

%!TEX TS-program = xelatex
\documentclass[10pt,oneside]{article}
\usepackage[fontsize=9pt]{scrextend}

@@

\geometry{includemp,
            letterpaper,
            top=1.0in,
            bottom=2.510cm,
            inner=0.5in,
            outer=0.4in,
            marginparwidth=2.1in,
            marginparsep=0.3in}

@@

The title is a field in the \texttt{metadata.json}:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{}
    \DataTypeTok{"title"}\FunctionTok{:} \StringTok{"Preprint template"}
\FunctionTok{\}}
\end{Highlighting}
\end{Shaded}
